Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 algorithm_intro.tex
edits through into of section 4

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item 
The conditional probability of pulling arm $i$ is less than
$1/\log(s)$ given the current estimates \ArmEV{t}{i'} of the arms'
attribute vectors.  In other words, we require
$\PullProb{t}{i} < 1/\log(s)$ where 
$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \mid \ArmEV{t}{i'}\ \forall i'}$
is the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
\end{itemize}

@@

The high-level idea in the proofs of our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret},
is the following.
Because the algorithm ensures that each arm is pulled
``frequently enough,''
the estimates \ArmEV{t}{i} become gradually more accurate in the
phase number $s$.
Thus, the fraction of agents who misidentify their best arm decreases.
Because for each arm, enough agents have a true preference for this
arm, once the arms' attribute vectors are learned well enough,
the algorithm will not need to incentivize any more,
resulting in a payment bound independent of $T$.
Similarly, the regret will decrease, and mostly accrue
due to ``problematic'' agents who are nearly tied in their preferences
between their top two arm choices.
The detailed analysis following this outline is somewhat subtle, though,
due to the dependence between the agents' arm pulls and the
estimates which in turn are based on past arm pulls.
We begin with several technical lemmas that are used for both the
payment and regret bounds.

To formally reason about the event that the estimates of arms'
attributes vectors are accurate enough --- or fail to be so ---
we define the events
$\AccE{t}{i}{j}{x} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x]$
that attribute $j$ of arm $i$ at time $t$ is estimated to
within accuracy $x$ or better.
Then, 
$\AccEU{t}{x} = \bigcap_{i,j} \AccE{t}{i}{j}{x}$
is the event that at time $t$, all arm attribute
estimates are accurate to within $x$ simultaneously.
We will show that for suitable choices of $t, x$,
the events \AccE{t}{i}{j}{x}
(and hence, by union bound, \AccEU{t}{x})
have high probability,
and that when they do, myopic agents do not make large mistakes.

>>>>

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item 
The conditional probability of pulling arm $i$ is less than
$1/\log(s)$ given the current estimates \ArmEV{t}{i'} of the arms'
attribute vectors.  In other words, we require
$\PullProb{t}{i} < 1/\log(s)$ where 
$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \mid \ArmEV{t}{i'}\ \forall i'}$
is the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
\pfedit{(Our assumption of a continuous noise distribution and one free pull ensure that 
ties in $\AgV \cdot \ArmEV{t}{i}$ between arms occur with probability $0$.)} 
\end{itemize}

@@

The high-level idea in the proofs of our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret},
is the following.
Because the algorithm ensures that each arm is pulled
``frequently enough,''
the estimates \ArmEV{t}{i} become gradually more accurate in the
phase number $s$.
Thus, the fraction of agents who misidentify their best arm decreases.
Because \pfedit{each arm has enough agents that prefer its true attribute vector}, 
once the arms' attribute vectors are learned well enough
the algorithm will not need to incentivize any more,
resulting in a payment bound independent of $T$.
Similarly, \pfedit{instantaneous} regret will decrease, and mostly accrue
due to ``problematic'' agents who are nearly tied in their preferences
between their top two \pfedit{arms}.
The detailed analysis following this outline is \pfedit{complicated by}
dependence between the agents' arm pulls and the
estimates which in turn are based on past arm pulls.
We begin with several technical lemmas that are used for both the
payment and regret bounds.

To formally reason about the event that the estimates of arms'
attributes vectors are accurate enough --- or fail to be so ---
we define the events
$\AccE{t}{i}{j}{x} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x]$
that attribute $j$ of arm $i$ at time $t$ is estimated to
within accuracy $x$ or better.
Then, 
$\AccEU{t}{x} = \bigcap_{i,j} \AccE{t}{i}{j}{x}$
is the event that at time $t$, all arm attribute
estimates are accurate to within $x$ simultaneously.
We will show that for suitable choices of $t, x$,
the events \AccE{t}{i}{j}{x}
(and hence, by \pfedit{a} union bound, \AccEU{t}{x})
have high probability,
and that when they do, myopic agents do not make large mistakes.
